% !TeX program = xelatex
\documentclass[11pt,a4paper]{article}

% --- Fonts & Engine Setup (XeLaTeX) ---
\usepackage{fontspec}
\usepackage[default]{sourcesanspro}
\usepackage{microtype}

% --- Layout & Styling ---
\usepackage[none]{hyphenat}
\usepackage[left=1in,top=0.8in,right=1in,bottom=0.8in]{geometry} % Standard letter margins
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{fontawesome5}
\usepackage{parskip} % Adds space between paragraphs automatically

% --- Force Justification + No Hyphenation ---
\tolerance=1
\emergencystretch=\maxdimen % Allows spaces to stretch to fill the line
\hyphenpenalty=10000        % Disables hyphenation
\hbadness=10000             % Suppresses "Underfull \hbox" warnings

% --- Colors (Same as CV) ---
\definecolor{primaryColor}{RGB}{30, 50, 80}
\definecolor{linkColor}{RGB}{0, 0, 150}

% --- Setup Hyperlinks ---
\hypersetup{
    colorlinks=true,
    linkcolor=linkColor,
    filecolor=linkColor,
    urlcolor=linkColor,
}

\begin{document}

% --- Header (Same as CV) ---
\begin{center}
    {\Huge \textbf{ANUBHAVSINGH SAWDAGUR}} \\[4pt]
    {\Large \textls[50]{PhD Candidate | AI Researcher | Cybersecurity Specialist}} \\[6pt]

    \small
    \faMapMarker*\enspace Bras D'eau, Mauritius \quad | \quad
    \faPhone*\enspace +230 570 22654 \quad | \quad
    \faEnvelope\enspace \href{mailto:anubhav_s@outlook.com}{anubhav\_s@outlook.com} \quad | \quad
    \faGithub\enspace \href{https://github.com/Anu-bhav}{github.com/Anu-bhav}
\end{center}

\vspace{20pt}
\hrule
\vspace{20pt}

% --- Date ---
\noindent 23 November 2025

\vspace{10pt}

% --- Subject Line ---
\noindent \textbf{RE: Inquiry regarding opportunities in AI, Cybersecurity, and Engineering}

\vspace{10pt}

% --- Salutation ---
\noindent Dear Hiring Team,

\vspace{10pt}

% --- Body Content ---
I am writing to introduce my profile as a specialist working at the intersection of \textbf{Advanced Artificial Intelligence} and \textbf{Offensive Cybersecurity}. With a career starting in 2018 that blends academic research with practical operational experience, I bring a multidisciplinary perspective that uses machine learning to solve complex problems while maintaining strict security standards.

My experience focuses on three core areas:

\textbf{1. Advanced AI \& Research Innovation:} \\
As a PhD Candidate, I am currently building "Multi-AI" systems designed for high-volatility markets. My work goes beyond theory; I focus on the practical implementation of various neural networks, including \textbf{Transformers, Deep Reinforcement Learning (DRL), LSTMs, RNNs, CNNs, and MLPs}. I specialise in selecting and optimising the right model for the specific task at hand, solving challenges related to non-stationary data to create adaptive, automated decision-making systems.

\textbf{2. Offensive Security \& Digital Forensics:} \\
My background is built on offensive security operations and forensic investigation. I have deep hands-on experience with industry-standard ecosystems, using \textbf{Kali Linux} for full-scope \textbf{penetration testing} and vulnerability assessments against the \textbf{OWASP Top 10} framework. Additionally, I am proficient with digital forensics tools like \textbf{EnCase} and \textbf{XRY} for conducting detailed investigations. Currently working towards my \textbf{OSCP} certification, I approach security with a "Red Team" mindset—understanding exactly how systems are compromised in order to defend them better.

\textbf{3. Engineering \& Leadership:} \\
Beyond research, I am also an educator and technical strategist. My experience ranges from full-stack development (C\#, ASP.NET) to leading the Advanced Networking and Security curriculum at the \textbf{IT Academy}. In this role, I designed training modules that prepared students for real-world \textbf{network defence}, ensuring they mastered the details of secure infrastructure and threat mitigation.

I am looking for a challenging role where I can combine these skills—one where I can use my ability to develop intelligent strategies that are efficient, data-driven, and mathematically sound.

I would welcome the opportunity to discuss how this hybrid expertise can add value to your organisation. Thank you for your time and consideration.

\vspace{20pt}

% --- Sign-off ---
\noindent Yours sincerely,

\vspace{20pt}

\noindent \textbf{Anubhavsingh Sawdagur}

\end{document}
