% !TeX program = xelatex
\documentclass[10pt,a4paper]{article}

% --- Fonts & Engine Setup (XeLaTeX) ---
\usepackage{fontspec}
\usepackage[default]{sourcesanspro}
\usepackage{microtype}

% --- Layout & Styling ---
\usepackage[none]{hyphenat}
\usepackage[left=0.5in,top=0.4in,right=0.5in,bottom=0.4in]{geometry}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{fontawesome5}
\usepackage{tabularx}

% --- Force Justification + No Hyphenation ---
\tolerance=1
\emergencystretch=\maxdimen % Allows spaces to stretch to fill the line
\hyphenpenalty=10000        % Disables hyphenation
\hbadness=10000             % Suppresses "Underfull \hbox" warnings

% --- Colors ---
\definecolor{primaryColor}{RGB}{30, 50, 80}
\definecolor{linkColor}{RGB}{0, 0, 150}

% --- Setup Hyperlinks ---
\hypersetup{
    colorlinks=true,
    linkcolor=linkColor,
    filecolor=linkColor,
    urlcolor=linkColor,
    pdftitle={Anubhavsingh Sawdagur - CV},
    pdfauthor={Anubhavsingh Sawdagur}
}

% --- Section Headings ---
\titleformat{\section}
{\Large\bfseries\color{primaryColor}\uppercase}
{}
{0em}
{}
[\titlerule]

\titlespacing*{\section}{0pt}{10pt}{6pt}

% --- Custom Commands ---
\newcommand{\entry}[4]{
    \noindent \textbf{#1} \hfill \textit{#2} \\
    \noindent \textit{#3} \hfill #4 \par
    \vspace{2pt}
}

\newcommand{\research}[3]{
    \noindent \textbf{#1} \hfill \textit{#2} \par
    \vspace{0pt}
    #3 \par
    \vspace{3pt}
}

\begin{document}

\pagestyle{empty}

% --- Header ---
\begin{center}
    {\Huge \textbf{ANUBHAVSINGH SAWDAGUR}} \\[4pt]
    {\Large \textls[50]{PhD Candidate | AI Researcher | Cybersecurity Specialist}} \\[6pt]

    \small
    % \enspace forces a horizontal space after the icon
    \faMapMarker*\enspace Bras D'eau, Mauritius \quad | \quad
    \faPhone*\enspace +230 5702 2654 \quad | \quad
    \faEnvelope\enspace \href{mailto:anubhav_s@outlook.com}{anubhav\_s@outlook.com} \quad | \quad
    \faGithub\enspace \href{https://github.com/Anu-bhav}{github.com/Anu-bhav}
\end{center}

\vspace{2pt}

% --- Executive Profile ---
\section*{Executive Profile}

\noindent \textbf{Dual-Domain Specialist} with a professional engineering track record \textbf{spanning since 2018}, merging \textbf{Offensive Cybersecurity} with \textbf{Artificial Intelligence}. Currently advancing the field of automated decision-making systems through PhD research on condition-adaptive trading strategies (LSTM/Transformers).

\noindent Renowned for a rigorous analytical approach and the ability to bridge the gap between academic theory and industry application. Dedicated to solving non-stationary data challenges through rigorous stochastic modeling and secure code implementation.

% --- Research & Innovation ---
\section*{Research \& Innovation}

\research{PhD Research: AI-Enhanced Adaptive Trading Frameworks}{University of Mauritius | Sep 2025 -- Present}
{
    \begin{itemize}[noitemsep,topsep=2pt,leftmargin=1.2em]
        \item \textbf{The Challenge:} Traditional algorithmic trading fails during "regime shifts" (e.g., market crashes or volatility spikes).
        \item \textbf{The Innovation:} Developing a \textbf{"Multi-AI" Ecosystem} that operates exclusively on technical indicators. The system utilizes a "Master Strategy" algorithm to autonomously switch between specialized neural networks (LSTM vs. MLP) based on real-time market state detection.
        \item \textbf{Key Tech:} Python, Deep Reinforcement Learning (DRL), Transformers, Volatility Modeling.
    \end{itemize}
}

\research{BSc Capstone: Automated Web Application Auditing Framework}{Leeds Beckett University | 2020}
{
    \begin{itemize}[noitemsep,topsep=2pt,leftmargin=1.2em]
        \item \textbf{The Innovation:} Architected an \textbf{Automated Web Application Auditing Framework with AI Integration}.
        \item \textbf{Technical Approach:} Designed intelligent, rule-based automation logic to autonomously scan, detect, and classify web vulnerabilities (SQLi, XSS) without human intervention.
        \item \textbf{Impact:} This research was pivotal in achieving \textbf{First Class Honours} and receiving the university's highest academic distinction.
    \end{itemize}
}

% --- Technical Arsenal ---
\section*{Technical Arsenal}
\renewcommand{\arraystretch}{1.2}
\begin{tabularx}{\textwidth}{@{}l X@{}}
    \textbf{AI \& Quantitative Analysis} & Deep Reinforcement Learning (DRL), LSTM, Transformers, Ensemble Learning, Bayesian Hyperparameter Tuning (Hyperopt), Feature Engineering. \\
    \textbf{Cybersecurity Operations} & Penetration Testing, Incident Response, Digital Forensics, Malware Analysis, AV Evasion, OWASP Top 10, Privilege Escalation (Linux/Windows). \\
    \textbf{Development \& Scripting} & \textbf{Python} (Pandas, NumPy, Scikit-Learn, PyTorch), \textbf{Bash Scripting}, C\# (MVC Framework), PHP (Laravel), SQL, RESTful APIs. \\
    \textbf{Infrastructure} & Docker Containerization, VMware Virtualization, Linux/Windows Server Administration, Secure Network Architecture. \\
\end{tabularx}

% --- Core Competencies ---
\section*{Core Competencies \& Leadership}
\begin{itemize}[noitemsep,topsep=0pt,leftmargin=1.2em]
    \item \textbf{Technical Pedagogy:} Proven ability to simplify complex concepts (Cryptography, Routing Protocols) for diverse audiences, derived from 6+ years of lecturing experience.
    \item \textbf{Research Communication:} Skilled in writing high-level technical proposals and documentation, bridging the gap between academic theory and practical application.
    \item \textbf{Strategic Problem Solving:} Expertise in designing architectural solutions that balance performance with security compliance.
    \item \textbf{Mentorship:} Experienced in guiding students through capstone projects and fostering a collaborative research environment.
\end{itemize}

% --- Professional Experience ---
\section*{Professional Experience}

\entry{Lecturer: Advanced Networking \& Security Curriculum}{Mar 2019 -- Present}{IT Academy}{Mauritius}
\begin{itemize}[noitemsep,topsep=2pt,leftmargin=1.2em]
    \item \textbf{Subject Matter Expert:} Solely responsible for delivering the \textbf{Advanced Networking and Security} syllabus.
    \item \textbf{Curriculum Design:} Modernized teaching materials to include practical labs on Network Defense, Routing Architectures, and Switching Protocols.
    \item \textbf{Impact:} Consistently commended by directorship for high student engagement and the ability to adapt teaching styles to individual learning needs.
\end{itemize}

\entry{Full-Stack Software Developer}{Jan 2018 -- Feb 2019}{Infini Tech Ltd}{Mauritius}
\begin{itemize}[noitemsep,topsep=2pt,leftmargin=1.2em]
    \item \textbf{Secure Development:} Engineered enterprise-grade web applications using \textbf{C\# and ASP.NET MVC}. Focused heavily on "Security by Design" to mitigate SQL Injection and XSS risks.
    \item \textbf{Database Architecture:} Managed complex schemas on \textbf{MSSQL and Oracle} platforms, optimizing query performance for high-volume data processing.
    \item \textbf{Enterprise Integration:} Implemented Windows Authentication protocols for seamless internal Identity Management.
\end{itemize}

% --- Education ---
\section*{Education}
\entry{Doctor of Philosophy (MPhil/PhD) in Information Systems}{Enrolled: Sep 2025}{University of Mauritius}{Réduit}
{ \noindent \small Focus: \textit{Machine Learning Applications in Financial Markets.} \par }
\vspace{4pt}

% Now this entry returns to normal size automatically
\entry{B.Sc. (Hons) Computer Forensics (First Class Honours)}{Graduated: 2020}{Leeds Beckett University (UK)}{}
{ \noindent \small Focus: \textit{Forensics Analysis and Offensive Security.} \par }

% --- Honours & Certifications ---
\section*{Honours \& Certifications}
\begin{itemize}[noitemsep,topsep=0pt,leftmargin=1.2em]
    \item \textbf{Outstanding Achievement Award (2020):} Awarded by Leeds Beckett University for exceptional academic performance and technical excellence in Computer Forensics.
    \item \textbf{Offensive Security Certified Professional (OSCP):} \textit{Candidate (In Progress)}.
\end{itemize}

% --- References ---
\section*{References}
\noindent
\begin{minipage}[t]{0.33\textwidth}
    \textbf{Dr. Raj Kishen Moloo} \\
    \small Associate Professor \\
    University of Mauritius \\
    \href{mailto:r.moloo@uom.ac.mu}{r.moloo@uom.ac.mu}
\end{minipage}%
\begin{minipage}[t]{0.33\textwidth}
    \textbf{Dr. Irfaan M. Coonjah} \\
    \small Director, IT Academy \\
    +230 5803 1000 \\
    \href{mailto:irfaan.coonjah@gmail.com}{irfaan.coonjah@gmail.com}
\end{minipage}%
\begin{minipage}[t]{0.33\textwidth}
    \textbf{Dr. Priya R. Essoo} \\
    \small Academic Director \\
    Rushmore Business School \\
    \href{mailto:priya.ramluggun-essoo@rbs.ac.mu}{priya.ramluggun-essoo@rbs.ac.mu}
\end{minipage}

\end{document}
